Stock enhancement undermines ecological community stability

### 2022-02-21 rmd/supporting_info.Rmd
edit: minor error

Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**). We identified five influential parameters (**Table S2-S4**), different values of which were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`). This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

>>>>

Prior to the main simulation, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement (see **Supplementary text**). We identified five influential parameters (**Table S2-S4**), of which different values were considered in the main simulation as follows: intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), carrying capacity ($K=$ `r unique(param_set$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`). This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.
